---
title: "select ckd population"
format: html
---

## Identify CKD population 2017-2020

This code is useable for the sql-uks-dme-01 database

```{r}
#| label: library
#| echo: false
#| message: false
#| warning: false

library(DBI)
library(odbc)
library(gt)
library(gtsummary)
library(ggplot2)
library(readr) 
library(data.table)
library(tidyr)
library(pyramid)
library(dplyr)
```

```{r}



```

### Kidney related codes

The following selection are people with Kidney related codes.

These have been selected by searching for kidney, gfr, acr and ckd.

```{sql connection = con}
drop table if exists Client_BTP_RW.DOH100_PCAM


  
select * into [Client_BTP_RW].[DOH100_PCAM]

 from client_BTP_RW.DOH101_PCA
union all 
select * from client_BTP_RW.DOH101_PCAa
union all
select * from client_BTP_RW.DOH101_PCAb
union all 
select * from client_BTP_RW.DOH101_PCAc
```

## Tracking patients with kidney diagnoses 2023-2025

```{sql connection=con, output.var="M2_results"}

#| echo: false  

drop table if exists Client_BTP_RW.DOH101_CKDpopn


  
select   Pseudo_NHS_Number,  PCA.ConceptID,  Date,  Value,  Type,  C.Term 

 into [Client_BTP_RW].[DOH101_CKDpopn]  
   
from  
  client_BTP_RW.DOH101_PCA
 as PCA 


left join client_BTP_RW.DOH101_codelist as C 
on   PCA.ConceptID = C.ConceptID  

where    
Term like '%chronic kidney%'    
or Term like '%ckd%'   
or Term like '%gfr%'   
or Term like '%albuminur%'   
or Term like '%ACR%'
or Term like '%nephr%'
or Term like  '%rena%'
or Term like  '%fgs%';
```

Having identified patients with the codes,

now add the patient details and the kidney codes

```{sql connection = con, output.var = "M1_results" }

select 
 P.Pseudo_NHS_Number
--,MAX(case when left(GPPracticeCode,1)='V' then '0' else left(GPPracticeCode,6) end) 
	,P.X_CCG_OF_REGISTRATION
    ,P.X_CCG_OF_RESIDENCE
	,P.Dob
	,cast(datediff(d,cast(Dob+'-15' AS date),getdate())/365.25 AS int) as Age
	,P.Sex
	,P.InterpreterRequired
  ,P.LSOA_Code
 -- ,0
	,P.IMD_Score
	--,''
	,P.LAT
	,P.LONG
 -- ,P.max(FrailtyScore) as FrailtyScore
	--,'' as FrailtyLevel
  ,ConceptID
  ,  CKD.Date
  ,  Value
  ,  Type
  ,  Term 


from 
  client_BTP_RW.DOH101_CKDpopn as CKD

left join
  client_BTP_RW.DOH001_MPI as P
on 
CKD.Pseudo_NHS_Number = P.Pseudo_NHS_Number



```

```{r}
#| echo: false 
#|  message: false 
#|  warning: false 
#M1_results <- M2_results
M1_results <- as.data.frame(M1_results) 
#M1_results <- group_by(M1_results$Pseudo_NHS_Number)
#head(M1_results)

head(M1_results)

M1_results$X_CCG_OF_RESIDENCE <- as.factor(M1_results$X_CCG_OF_RESIDENCE ) 
M1_results$Pseudo_NHS_Number <- as.factor(M1_results$Pseudo_NHS_Number ) 
M1_results$X_CCG_OF_REGISTRATION <- as.factor(M1_results$X_CCG_OF_REGISTRATION ) 
M1_results$Sex <- as.factor(M1_results$Sex ) 
M1_results$IMD_Score <- as.integer(M1_results$IMD_Score)
M1_results$InterpreterRequired <- as.factor(M1_results$InterpreterRequired)
M1_results$Age <- as.integer(M1_results$Age)
#M1_results$Agegrp <- as.factor((M1_results$Agegrp))

#M1_results$EthnicMainGroup <- as.factor(M1_results$EthnicMainGroup ) 
M1old <- M1_results[M1_results$Age >= 18,] 
M1older<- M1_results[M1_results$Age >= 35,] 

summary(M1_results$X_CCG_OF_RESIDENCE)
```

```{r}
# use cut to produce age group table
M1_results$Agegrp <- cut(M1_results$Age, 
                           breaks = c(0,5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,150),
                           labels = c("0-4","5-9","10-14","15-19","20-24","25-29","30-34","35-39","40-44","45-49","50-54","55-59","60-64","65-69","70-74","75-79","80-84","85-89","90+"),
                           right = FALSE
)
```

```{r}
#| echo: false 
#| message: false
#| warning: false 
 # to make population pyramid 
Pyramid1 <- M1_results[,c("Agegrp","Sex")]  
Pyramid1 <- setDT(Pyramid1)[,.N, keyby= c("Agegrp","Sex")] 
Pyramid1 <- as.data.frame(Pyramid1) 

#Pyramid1 %% pivot_wider(names_from = Pyramid1$Sex , values_from = Pyramid1$N )  
Pyramid1 <- reshape(Pyramid1, idvar = "Agegrp", timevar = "Sex", direction = "wide" ) 
colnames(Pyramid1)[colnames(Pyramid1)== "N.F"] <- "female" 
colnames(Pyramid1)[colnames(Pyramid1)== "N.M"] <- "male" 

Pyramid1 <- Pyramid1[,c("male","female","Agegrp")] 

 pyramid(Pyramid1, main = "Population Pyramid for CKD C&M ICB ", Laxis = seq(0,200000, len=5))    

#Pyramid1   

#4% *2347979 = 93,919.16  #7% * total pop = 114,392.81
```

The whole population contains people approximately 50% M/F

```{r}
```

```{r}
#| echo: false
#|   message: false 
#|   warning: false 

#tbl_summary(M1_results)


head(M1_results) 
M1_results$ConceptID <- as.factor(M1_results$ConceptID)  
M1_results$Value <- as.integer(M1_results$Value) 
M1_results$Pseudo_NHS_Number <- as.factor(M1_results$Pseudo_NHS_Number) 
M1_results$Type <-as.factor(M1_results$Type)





summary(M1_results$eGFR)
unique(M1_results)
str(M1_results)
M1_results %>% group_by(Pseudo_NHS_Number) %>% filter(CKD == TRUE)
summary(M1_results$Pseudo_NHS_Number)
```

```{r}
#kidney <- M1_results %>%    select( Date, Value,Term) 

#kidney %>% 
 # tbl_summary(  ) %>%   
  #bold_labels() %>%   
  #italicize_levels()
```

These have been further selected by single codes which are the most frequently used. That is eGFR EPI and CKD.

```{r}
#| echo: false
#| message: false
#| warning: false
## the egfrtab isolates all rows where there is an egfr
## the ckdtab isolates all rows where there is a ckd3 code

egfrtab <- M1_results[M1_results$ConceptID == '1011481000000105',]
#pt1 <- egfrtab[  egfrtab$Pseudo_NHS_Number == '719C0A9DA6D3EF4AF01F384FC473C92BE449CBFBA55D11E3234166259B00D6A3', ]  
 M1_results$CKD = ifelse(M1_results$ConceptID == '433144002',TRUE,FALSE)
 M1_results$eGFR = ifelse(M1_results$ConceptID == '1011481000000105',TRUE,FALSE)
 
summary(egfrtab)




```

```{r}
# use cut to produce age group table
egfrtab$Agegrp <- cut(egfrtab$Age, 
                           breaks = c(0,5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,150),
                           labels = c("0-4","5-9","10-14","15-19","20-24","25-29","30-34","35-39","40-44","45-49","50-54","55-59","60-64","65-69","70-74","75-79","80-84","85-89","90+"),
                           right = FALSE
)
# to make population pyramid 
Pyramid1 <- egfrtab[,c("Agegrp","Sex")]  
Pyramid1 <- setDT(Pyramid1)[,.N, keyby= c("Agegrp","Sex")] 
Pyramid1 <- as.data.frame(Pyramid1) 

#Pyramid1 %% pivot_wider(names_from = Pyramid1$Sex , values_from = Pyramid1$N )  
Pyramid1 <- reshape(Pyramid1, idvar = "Agegrp", timevar = "Sex", direction = "wide" ) 
colnames(Pyramid1)[colnames(Pyramid1)== "N.F"] <- "female" 
colnames(Pyramid1)[colnames(Pyramid1)== "N.M"] <- "male" 

Pyramid1 <- Pyramid1[,c("male","female","Agegrp")] 

 pyramid(Pyramid1, main = "Population Pyramid for egfr C&M ICB ", Laxis = seq(0,200000, len=5))    



```

```{r}

```

```{r}
# use cut to produce age group table
ckdtab$Agegrp <- cut(ckdtab$Age, 
                           breaks = c(0,5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,150),
                           labels = c("0-4","5-9","10-14","15-19","20-24","25-29","30-34","35-39","40-44","45-49","50-54","55-59","60-64","65-69","70-74","75-79","80-84","85-89","90+"),
                           right = FALSE
)

# to make population pyramid 
Pyramid1 <- ckdtab[,c("Agegrp","Sex")]  
Pyramid1 <- setDT(Pyramid1)[,.N, keyby= c("Agegrp","Sex")] 
Pyramid1 <- as.data.frame(Pyramid1) 

#Pyramid1 %% pivot_wider(names_from = Pyramid1$Sex , values_from = Pyramid1$N )  
Pyramid1 <- reshape(Pyramid1, idvar = "Agegrp", timevar = "Sex", direction = "wide" ) 
colnames(Pyramid1)[colnames(Pyramid1)== "N.F"] <- "female" 
colnames(Pyramid1)[colnames(Pyramid1)== "N.M"] <- "male" 

Pyramid1 <- Pyramid1[,c("male","female","Agegrp")] 

 pyramid(Pyramid1, main = "Population Pyramid for CKD C&M ICB ", Laxis = seq(0,20000, len=5))    

```

```{r}
#| echo: false 
#|  message: false 
#|  warning: false 
#library(ggplot2) 
egfrtab <- as.data.table(egfrtab[egfrtab$Value < 30,]  )
head(egfrtabs)
egfrtabs <- egfrtab[Age == 80,]


ggplot(data = egfrtabs, aes(y = Value, x =  Date, group = Pseudo_NHS_Number))+   geom_line(  )
```

0all
