---
title: "whole cohort"
format: html
---

## whole cohort

This page is to display the egfr trends 


```{r}
library(readr)
library(ggplot2)
library(dplyr)
```

The first set is those surprisingly few with egfr < 30 but no ckd code
```{r}

nockdegfr <- read_csv("P:/CKDMH/Secure_data/nockdegfr.csv", 
    col_types = cols(ConceptID = col_character()))
View(nockdegfr)
```

```{r}


nockdegfr %>%
 filter( daysSinceFirst <120, daysSinceFirst > -1) %>%
ggplot(data =,aes(x= daysSinceFirst, y = value_num, group = Pseudo_NHS_Number, colour = Pseudo_NHS_Number)) + geom_line()+theme(legend.position = "none")
```


```{r}
wholeegfr_cohort <- read_csv("P:/CKDMH/Secure_data/wholeegfr cohort.csv", col_types = cols(ConceptID = col_character()))
```


```{r}


wholeegfr_cohort %>%
 filter( daysSinceFirst <120, daysSinceFirst > -1, value_num < 90) %>%
ggplot(data =,aes(x= daysSinceFirst, y = value_num, group = Pseudo_NHS_Number, colour = Pseudo_NHS_Number)) + geom_line()+theme(legend.position = "none")
```
